The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-16 manuscript/manuscript.Rnw
show the shape of the core placenta transcriptome

>>>>

\begin{figure}
<<core.placenta.transcriptome.distribution,fig.width=8,fig.height=8,out.height="0.8\\textheight",echo=FALSE,message=FALSE>>=
cpt.distribution.shape <- 
    data.table(melt(
        core.placenta.transcriptome.genes.shape[fifth_min_expression > 0,
                                                list(human_name,
                                                     min_expression,
                                                     second_min_expression,
                                                     third_min_expression,
                                                     fourth_min_expression,
                                                     fifth_min_expression)],
               id.vars="human_name",
               variable.name="Lowest Expression",
               value.name="Expression (FPKM)"
               ))
cpt.distribution.shape <- 
    cpt.distribution.shape[,`Lowest Expression`:=
                               gsub("^min_expression$","First",
                                    `Lowest Expression`)]
cpt.distribution.shape <- 
    cpt.distribution.shape[,`Lowest Expression`:=
                               factor(gsub("^(.)(.+)_min_expression$","\\U\\1\\L\\2",
                                           `Lowest Expression`,perl=TRUE),
                                      levels=c("First","Second","Third","Fourth","Fifth"))
                           ]
print(ggplot(cpt.distribution.shape[`Expression (FPKM)` > 0,],
             aes(x=`Expression (FPKM)`+1,color=`Lowest Expression`))
      + geom_histogram(aes(y=..count..+1))
      + xlab(expression(FPKM+1))
      + ylab("Genes with N-th Lowest Expression + 1")
      + scale_y_log10()
      + scale_x_log10())
@ 
\caption{Distribution shape of placenta core genes. A histogram and
  density plot of the first through fifth lowest expression in each of
  \Sexpr{star.logs[,length(unique(species))]} species for each of
  \Sexpr{nrow(core.placenta.transcriptome.genes.shape)} human ortholog
  genes.}
\label{fig:core_placenta_transcriptome_shape}
\end{figure}
